Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-20 paper/ms.tex
new names

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
%=========================================================================
%		EXTERNAL PACKAGES
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
%\usepackage[section]{placeins}
\usepackage {graphicx}
%\usepackage{graphics}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}
\pdfminorversion=5

@@

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
\newcommand{\apj}{ApJ}  
\newcommand{\apjs}{ApJS}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\lmmin}{{\ifmmode{{\log M_{\rm min}}}\else{${\log M_{\rm min}}$}\fi}}
\newcommand{\lmmax}{{\ifmmode{{\log M_{\rm max}}}\else{${\log M_{\rm max}}$}\fi}}

@@

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3$}
\author[J. Mejia-Restrepo and J.E. Forero-Romero]{\parbox[t]{\textwidth}{\raggedright 
  J. Mejia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}
\vspace*{6pt}\\
$^1,^3$Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile\\
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

\maketitle

\begin{abstract}
We present
\end{abstract}

\begin{keywords}
Cosmology: theory - large-scale structure of Universe -
Methods: data analysis - numerical - N-body simulations
\end{keywords}

@@

The goal becomes finding the typical DM halo mass of halos hosting LAES.
In the case of LAEs there are different ways to find this mass range.
One approach is theoretical, using general astrophysical principles to find the relationship between halo mass, intrinsic \ly\ luminosities and observed \ly\ luminosities. This approach is usually implemented through semi-analytic models \citep{Garel2012,Orsi2012} and  full N-body hydrodynamical simulations \citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012}.

@@

Throughout this letter we assume a $\Lambda$CDM cosmology with the
following values for the cosmological parameters, $\Omega_{m}=0.27$,
$\Omega_{\Lambda}=0.73$ and $h=0.70$, corresponding to the matter
density, vacuum density and the Hubble constant in units of 100 km
s$^{-1}$ Mpc$^{-1}$.

@@

\begin{figure*}
\includegraphics[width=0.99\textwidth]{likelyplot_1deg_total.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degf.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdM.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdMf.png}
\caption{Likelihood}
\label{fig:like}
\end{figure*}

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA and a flux limit
of $2\times10^17{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using spectroscopy they found a 22\% contamination fraction.
Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
NB497  narrow-band filter whose 77\AA FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc  and 82\hMpc comoving, respectively.

@@

We use results from the \todo Bolshoi simulation \citep{Bolshoi}\toref which was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. The dark matter distribution was sampled using \todo $2048^{3}$ particles. The cosmological parameters are consistent with a Wilkinson Microwave Anisotropy Probe (WMAP) ninth year data \todo PLANK? (\toref) with a matter density
$\Omega_{\rm m} = 0.307$, cosmological constant
$\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.70$, slope
of the power spectrum \todo $n=0.95$ and normalization of the power
spectrum\todo $\sigma_{8}=0.82$ \todo.  
This translates into a particle mass of \todo $m_{\rm p}=1.54\times 10^{8}$ $h^{-1}$ M$_{\odot}$.

We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
Multidark database \todo \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
halo in the box we extract its comoving position and mass. 
We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun resolved with at least  $10$ particles.
%the reasons for this choice are explained in the next sub-section.

@@

The occupation fraction varies along  the mock fields tracing the cosmic variance changing in a factor $\sim 2$ ($\sim 0.3$, see left panel in Fig. \ref{fig:cosmicv}). The interpretation of the occupation fraction $f_{\rm occ}$ involves two phenomena: the actual presence of a star forming galaxy in a halo and its detectability as a LAE.

@@

\subsection{Constraining \mmin, \mmax and \focc in DHM hosting LAEs}

In Fig. \ref{fig:like} the posterior probability distributions in the \mmin-\mmax, \mmin-\focc, \mmin-\dm, \mmax-\focc, \mmax-\dm and \focc-\dm\ parameter spaces. We find that the \mmin and \mmax parameter space cannot be well constrained mainly because of cosmic variance and the large observational Poisonnian uncertainty in the ACF. We however found that 10.0$<\log \mmin<$11.1 and 11.0$<\log\mmax<$12.8.   We interestingly find that \focc\ is basically completely determine by \mmin  going from \focc$=$0.015 when $\log\mmin=$10.0 to \focc$=$0.43 when $\log\mmin=$11.1. We remark that those models where $\log \focc>0.0$ ($\focc>1$) correspond 
to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number of LAEs in the universe due to cosmic variance.

\begin{figure}
\includegraphics[width=0.47\textwidth]{mmin_dev.png}
\includegraphics[width=0.47\textwidth]{corr.png}
\caption{Left: $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm 2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log M_{\rm max}$. The points are color coded by $\Delta \log M\left[\rm{M_{\odot}h^{-1} ]}\right]$. THe green line accounts for the 1:1 relation. Right: Angular Correlation functions for $\log M_{\rm min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta M$. The error bars represent the 1 sigma deviation due to cosmic variance.}
\label{fig:mmed}
\end{figure}

@@

In  the top panel of Fig. \ref{fig:mmed} we show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE halo mass as a function of \lmmin\ for each of the models that we run in our MCMC simulation.  The points are color coded according to their \dlm\ associated value. We can see that the median mass, $M_{50}$, and $M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially when $\dlm\gtrsim1.0$dex. We particularly found that  $\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that $\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$ regardless of the value of \dlm. The latter is a consequence of the very steepen distribution of the dark matter mass function  and is at the same time the reason for the almost perfect one to one relation between \mmin\ and \focc. However, it can also be seen in Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax ($\lmmin+0.2\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the clustering strength of models sharing the same \mmin but different \mmax should be mainly driven by the  $\sim16\%$ most massive  halos of each model $\mathcal{M}$.

In order to estimate the effect of most massive halos in  $ACF_{\mathcal{M}}$ in the bottom panel of Fig. \ref{fig:mmed} we show the computed $ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values of $\dlm$. We can see that the clustering gets stronger for larger values of \dlm. Nevertheless, due to the large impact of cosmic variance at the volume of the current observations all the models  are basically consistent within errors. The last result explain the current difficulty to put tighter constrains in \lmmax\ in our model.

\subsection{Constraining DMH mass with cosmic variance}
In the left panel of Fig. \ref{fig:cosmicv} we show the number halo distribution (NHD) in the  mock fields of the simulation for different models $\mathcal{M}$. By simple inspection one can infer an increase in the distribution with as \lmmin increase.  This trend is confirmed in the right panel of Fig. \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function of \lmmin. We particularly found that when we consider survey fields of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of the NHD increases monotonically from 0.05dex (0.10dex) when $\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$. The latter result opens the possibility to constrain the \lmmin (as well as the median mass) of LAEs by simply measure the width of the distribution of observed LAE along several observational fields mapping $\sim1{\rm deg^2}$ in area and the observational depth determined by the NB479 filter.

@@

\begin{figure}
\includegraphics[width=0.23\textwidth, height=0.19\textwidth]{ndist.png}
\includegraphics[width=0.23\textwidth, height=0.19\textwidth]{mmin_dfocc1.png}
\caption{Left: Halo number distribution  over the 54 mock field of the simulation for different models of $M_{\rm min}$-$M_{\rm max}$.Right:Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\rm halos}/\tilde{N}_{\rm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$. Points are color coded according to their associated value of $\Delta M \equiv M_{\rm min}-M_{\rm min}$. }
\label{fig:cosmicv}
\end{figure}

\bibliographystyle{mn2e}
\bibliography{references.bib}

>>>>

\documentclass{emulateapj} 
%\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e}

%External Packages and personalized macros
%=========================================================================
%		EXTERNAL PACKAGES
%=========================================================================
%\usepackage{amsmath} 
%\usepackage{amssymb} 
%\usepackage[section]{placeins}

\usepackage {graphicx}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphics}
\usepackage{epsfig}
\usepackage{float}
\bibliographystyle{apj}

\usepackage {graphicx}

%\usepackage{graphics}
%\usepackage[dvips]{epsfig}
%\usepackage{epsfig}  
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{caption}
%Non reposionated tables
%\usepackage{float}
\restylefloat{table}
%Multiple columns support for tables
\usepackage{array}
\usepackage{booktabs}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}
\pdfminorversion=5

@@

\newcommand{\LCDM}{$\Lambda$CDM~}
\newcommand{\beq}{\begin{eqnarray}}  
\newcommand{\eeq}{\end{eqnarray}}  
\newcommand{\zz}{$z\sim 3$} 
%\newcommand{\apj}{ApJ}  
%\newcommand{\apjs}{ApJS}  
%\newcommand{\apjl}{ApJL}  
%\newcommand{\aj}{AJ}  
%\newcommand{\mnras}{MNRAS}  
%\newcommand{\mnrassub}{MNRAS accepted}  
%\newcommand{\aap}{A\&A}  
%\newcommand{\aaps}{A\&AS}  
%\newcommand{\araa}{ARA\&A}  
%\newcommand{\nat}{Nature}  
%\newcommand{\physrep}{PhR}
%\newcommand{\pasp}{PASP}    
%\newcommand{\pasj}{PASJ}    
\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmin}{{\ifmmode{{M_{\rm min}}}\else{${M_{\rm min}}$}\fi}}
\newcommand{\mmax}{{\ifmmode{{M_{\rm max}}}\else{${M_{\rm max}}$}\fi}}
\newcommand{\lmmin}{{\ifmmode{{\log M_{\rm min}}}\else{${\log M_{\rm min}}$}\fi}}
\newcommand{\lmmax}{{\ifmmode{{\log M_{\rm max}}}\else{${\log M_{\rm max}}$}\fi}}

@@

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$}
\author{
  Juli\'an E. Mej\'ia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1,3}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

\affil{
$^1$Departamento de Astronom\'{i}a, Universidad de Chile, Camino el Observatorio 1515, Santiago, Chile\\
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
$^3$FACom-Instituto de F\'isica-FCEN, Universidad de Antioquia, Calle 70 No. 52-21, Medell\'in, Colombia
}

\begin{abstract}
We study the impact of cosmic variance and observational uncertainties in constraining the mass and  occupation fraction ($f_{\rm occ}$) of dark matter halos hosting \ly\ Emitting  Galaxies at high redshift (LAEs).
We use a N-body simulation to construct mock catalogs with the same typical size  of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$) to match the observed  angular correlation function (ACF) and number density of LAEs.  
In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm   max}$ can only host one detectable LAE at most. By following a thorough Markov Chain Monte-Carlo exploration of the parameter space determined by $M_{\rm min}$ and $M_{\rm   max}$, our analysis shows that $f_{\rm occ}$ is uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$ using the relation $\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$ . 
However, the current observational data only allows us to put weak constraints on $M_{\rm min}$, $M_{\rm max}$ and consequently on $f_{\rm occ}$. 
Particularly, we find that $10^{9.6}\hMsun\leq M_{\rm min}\leq 10^{11.0}\hMsun$ , $10^{10.9}\hMsun\leq M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\leq f_{\rm occ}\leq 0.30$. 
Nevertheless, we also find that  the upcoming large surveys can help to put tighter constraints on $M_{\rm min}$ and $f_{\rm occ}$ through the width measurement of the LAE number distribution function obtained over several fields of the same size of current observations. 
Analogously, the  improvement in the precision of the measured ACF will assist in constraining $M_{\rm max}$.  
\end{abstract}

\keywords{
Cosmology: theory - large-scale structure of Universe -
Methods: data analysis - numerical - N-body simulations
}

@@

The goal becomes finding the typical DM halo mass of halos hosting LAEs.
In the case of LAEs there are different ways to find this mass range.
One approach is theoretical, using general astrophysical principles to find the relationship between halo mass, intrinsic \ly\ luminosities and observed \ly\ luminosities. This approach is usually implemented through semi-analytic models \citep{Garel2012,Orsi2012} and  full N-body hydrodynamical simulations \citep{Laursen2007, Dayal2009, ForeroRomero2011, Yajima2012}.

@@

Throughout this letter we assume a $\Lambda$CDM cosmology with the
following values for the cosmological parameters, $\Omega_{m}=0.30711$,
$\Omega_{\Lambda}=0.69289$ and $h=0.70$, corresponding to the matter
density, vacuum density and the Hubble constant in units of 100 km
s$^{-1}$ Mpc$^{-1}$.

\begin{figure}
\includegraphics[width=0.46\textwidth, height=0.38\textwidth]{ndist.png}
\caption{Cumulative halo number distribution function over the 27 mock fields of the simulation for different models of $M_{\rm min}$-$M_{\rm max}$.}
\label{fig:cosmicv0}
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.99\textwidth]{likelyplot_1deg_total.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degf.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdM.png}
%\includegraphics[width=0.47\textwidth]{likelyplot_1degdMf.png}
\caption{One and two dimensional projections of the posterior probability distributions of \mmin, \mmax and \focc as described in the label of each sub-figure.}
\label{fig:like}
\end{figure*}

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
of $2\times10^17{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using spectroscopy they found a 22\% contamination fraction.
Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
NB497  narrow-band filter whose 77\AA FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc  and 82\hMpc comoving, respectively.

@@

We use results from the  Bolshoi simulation \citep{Bolshoi} which was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. The dark matter distribution was sampled using  $2048^{3}$ particles. The cosmological parameters are consistent with Planck 2013 results \citep{Planck2014} with a matter density
$\Omega_{\rm m} = 0.307$, cosmological constant
$\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.70$, slope
of the power spectrum  $n=0.96$ and normalization of the power
spectrum $\sigma_{8}=0.82$.  
This translates into a particle mass of  $m_{\rm p}=1.54\times 10^{8}$ $h^{-1}$ M$_{\odot}$.

We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
Multidark database  \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
halo in the box we extract its comoving position and mass. 
We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun resolved with at least  $10$ particles.
%the reasons for this choice are explained in the next sub-section.

@@

Fig. \ref{fig:cosmicv0}  shows the cumulative halo number distribution (HND) in the  mock fields of the simulation for different models $\mathcal{M}$. From this figure we can see that the number of dark matter halos along the mock fields for different models $\mathcal{M}$ varies within a factor of $\sim 2$ ($\sim 0.3$dex) tracing the cosmic variance. As a consequence, the occupation fraction varies along  the mock fields  by the same factor factor. The interpretation of the occupation fraction $f_{\rm occ}$ involves two phenomena: the actual presence of a star forming galaxy in a halo and its detectability as a LAE.

@@

\subsection{Constraining \mmin, \mmax\ and \focc\ in Dark Matter Halos hosting LAEs}

In Fig. \ref{fig:like} we present yhe one and two dimensional projections of the posterior probability distributions of \mmin, \mmax and \focc. We find that the \mmin and \mmax parameter space cannot be tightly constrained mainly because of cosmic variance and the large observational Poisonnian uncertainty in the ACF. We however found that 9.6$<\log \mmin<$11.0 and 10.9$<\log\mmax<$13.0.   We interestingly find that \focc\ is basically completely determined by \mmin  going from \focc$=$0.015 when $\log\mmin=$9.6 to \focc$=$0.30 when $\log\mmin=$11.0  ($\focc\sim0.1\left(\mmin/10^{10.5}\right)^{0.93}$). We remark that those models where $\log \focc>0.00$ ($\focc>1$) correspond 
to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number density of LAEs in the universe due to cosmic variance (see Fig. \ref{fig:cosmicv0}).%in the number of dark matter halos along the mock fields

\begin{figure}
\includegraphics[width=0.47\textwidth]{mmin_mmed_colordm.png}
\caption{ $\log M_{\rm min}$ vs $\log M_{\rm 50\%}$ (black), $\log M_{\rm 16\%}$-$\log M_{\rm 84\%}$ (blue) and  $\log M_{\rm 2.5\%}$-$\log M_{\rm 97.5\%}$(red) for different values of $\log M_{\rm max}$. The points are color coded by $\Delta \log M\left[\rm{M_{\odot}h^{-1} ]}\right]$. The green line diagonal line accounts for the 1:1 relation and the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin.}
\label{fig:mmed}
\end{figure}

@@

Previous  attempts to constrain the DMH mass of LAEs by means of the ACF   present their result in terms of the median mass of LAEs that is derived from the derived correlation length by means of semi-analitical prescriptions  \citep[e.g.][]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. Instead, in this work we directly compare the ACF of our simulated mock catalogs with the observational ACF and present our results in terms of a  minimum and maximum mass DMH hosting LAEs. It is therefore necessary to connect our approach by computing the median mass of the DMH in each of the models $\mathcal{M}$.  In   Fig. \ref{fig:mmed} we show the 50 ($\log M_{50}$, black dots), the 84 ($\log M_{84}$,blue diamonds) and 95 ($\log M_{95}$, red squares) percentiles of the LAE halo mass as a function of \lmmin\ for each of the models that we run in our MCMC simulation.  The points are color coded according to their \dlm\ associated value. We can see that the median mass ($M_{50}$) and $M_{84}$ are not very sensitive to  $\lmmax=\lmmin +\dlm$ specially when $\dlm\gtrsim1.0$dex. We particularly found that  $\lmmin\lesssim\log M_{50}\lesssim\lmmin+0.2\rm{dex}$ and that $\lmmin+0.1\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+0.5\rm{dex}$ regardless of the value of \dlm. The latter is a consequence of the very steepen distribution of the dark matter mass function  and is at the same time the reason for the almost perfect one to one relation between \mmin\ and \focc. However, it can also be seen in Fig. \ref{fig:mmed} that $\log M_{84}$ is very sensitive to \lmmax ($\lmmin+0.2\rm{dex}\lesssim\log M_{50}\lesssim\lmmin+1.5\rm{dex}$). Thereby, any differences in the clustering strength of models sharing the same \mmin but different \mmax should be mainly driven by the  $\sim16\%$ most massive  halos of each model $\mathcal{M}$.

In order to estimate the effect of most massive halos in  $ACF_{\mathcal{M}}$ in Fig. \ref{fig:corr} we show the computed $ACF_{\mathcal{M}}$ of models with $\lmmin=0.5$ and different values of $\dlm$. We can see that the clustering gets stronger for larger values of \dlm. Nevertheless, due to the large impact of cosmic variance at the volume of the current observations all the models  are basically consistent within errors. The last result together with the large Poissonian observational error in the ACF explain the current difficulty to put tighter constrains in \lmmax\ in our model.

 In Fig. \ref{fig:mmed} the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin that we previously obtained. From this figure we find that the median dark matter halo mass is $\tilde{M}_{\rm h} = 10^{10.6^{+0.7}_{-0.6}$. This result is consistent with previous estimations of  the  median dark matter halo mass reported by  \citet{Bielby16} ($\tilde{M}_{\rm h} = 10^{11.0\pm0.6}$), \citet{Gawiser07} ($\tilde{M}_{\rm h} = 10^{10.9\pm0.9}$) and \citet{Ouchi2010} ($\tilde{M}_{\rm h} = 6.7^{+42.0}_{6.7}\times10^{10}}$) using semi-analitical approaches.

\begin{figure}

\includegraphics[width=0.47\textwidth]{corr.png}
\caption{ Angular Correlation functions for $\log M_{\rm min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta M$. The error bars represent the 1 sigma deviation due to cosmic variance.}
\label{fig:corr}
\end{figure}

\subsection{Constraining Dark matter halos mass  with cosmic variance}
Fig. \ref{fig:cosmicv0}  shows the  halo number distribution (HND) in the  mock fields of the simulation for different models $\mathcal{M}$. By simple inspection one can infer an increase in the distribution with as \lmmin increase.  This trend is confirmed in Fig. \ref{fig:cosmicv}  where we plot the central 1-$\sigma$ (blue diamonds) and 2-$\sigma$  (red dots) widths  of the NDH as a function of \lmmin. We particularly found that when we consider survey fields of $\sim1{\rm deg^2}$, the central  1-$\sigma$ (2-$\sigma$) width of the HND increases monotonically from 0.05dex (0.10dex) when $\lmmin=9.5$ to 0.20dex (0.35dex) when $\lmmin=12.0$. The latter result opens the possibility to constrain the \lmmin (as well as the median mass) of LAEs by simply measure the width of the distribution of observed LAE along several observational fields mapping $\sim1{\rm deg^2}$ in area and the observational depth determined by the NB479 filter.

@@

\begin{figure}
\includegraphics[width=0.46\textwidth, height=0.33\textwidth]{mmin_dfocc1.png}
\caption{Width of the halo number distribution over the 54 mock field of the simulation ($\Delta \log \left( N_{\rm halos}/\tilde{N}_{\rm halos}\right)$) of the central 68 (blue diamonds) and  95(red circles)  percentiles vs $M_{\rm min}$. Points are color coded according to their associated value of $\Delta M \equiv M_{\rm min}-M_{\rm min}$. The green line diagonal line accounts for the 1:1 relation and the green vertical lines represent  the 16, 50 and 84 percentiles  of the posterior probability distribution of \mmin.}
\label{fig:cosmicv}
\end{figure}

\section{Conclusions}

In this letter we studied the impact of cosmic variance and observational uncertainties in constraining the mass range and  occupation fraction of dark matter halos hosting  LAEs.  
To this end, we used the BolshoiP N-body simulation to construct  27 mock fields  with the same typical size  of observed fields at  $z=3.1$ ($\sim 1 {\rm deg^2}$).  
In our model a dark matter halo with mass in the range $M_{\rm min}<M_{\rm h}<M_{\rm   max}$ can only host one detectable LAE at most. 
We explored the parameter space determined by \mmin\ and \mmax\ using Monte Carlo Markov-Chain minimization to match the observed  ACF and mean number density of LAEs.

Our analysis allowed us to put weak constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm occ}$ where $10^{9.7}\hMsun\leq \log M_{\rm min}\leq 10^{11.2}\hMsun$, $10^{10.9}\hMsun\leq \log M_{\rm max}\leq 10^{13.0}\hMsun$ and $0.02\hMsun\leq f_{\rm occ}\leq 0.5$, spanning three orders of magnitude in halo mass.
Previous works\citep{Hayashino2004, Gawiser07,Ouchi2008,Bielby16} have found typical masses within somehow narrower mass ranges ($\sim 10^{10.5}$-$10^{12}$).  
The main reason for our weaker constraints and large discrepancies with previous works resides in the cosmic variance on the typical field size in observations. 
A thorough exploration of cosmic variance impact as we present in this letter had not been presented so far in the literature.

Our analysis also allowed us to draw three results that can be used to put tighter constraints on $M_{\rm min}$, $M_{\rm max}$ and $f_{\rm occ}$ once upcoming large LAE surveys, as the HETDEX project \citep{Hetdex2011} and the HSC ultra deep survey, are available :
\begin{enumerate}
\item $f_{\rm occ}$ and the median mass of LAEs are almost uniquely determined by $M_{\rm min}$ regardless of $M_{\rm max}$. \item measuring the width of the LAE number distribution function obtained over several fields of $\approx 1$ deg$^2$ one will be able to tightly constrain  $M_{\rm min}$, $M_{\rm med}$ and $f_{\rm occ}$ up to a factor of  2. 
\item  $M_{\rm max}$ drives the ACF strength at short angular distances ($<1\,\rm arcmin$), therefore precise measurements of the ACF at such scales are crucial to accurately determine \mmax.
\end{enumerate}

\section*{Acknowledgments}

JM acknowledges ``CONICYT-PCHA/doctorado Nacional para extranjeros/2013-63130316'' for their PhD scholarship support.

\bibliographystyle{apj}
\bibliography{references.bib}
